\textcolor{blue}{A gradient-based optimization method for motion planning}$^{1}$

### 2016-01-28 answers-to-reviewers.tex

\noindent
\hrulefill\\

\subsection{Comment 6}

Section 3.5.1:
This section does not read a nicely as the previous. Simplifying the notation by using sub/super scripts to define the reference frame of points rather than having the long expression for u, may help a bit.

\vspace{0.5cm}

\textbf{Answer}:

We have rewritten the notations of this part to clarify it. We have used a subscript $loc$ to refer the local frames of the points, and a simplified matrix notation for the homogeneous matrix product. Thus the expressions of $\mathbf{u}$ and $g$ are clearer.

\noindent
\hrulefill\\

\subsection{Comment 7}

@@

\noindent
\hrulefill\\

\subsection{Comment 9}

Related to my previous comment about path pruning, then I would generally recommend people to use a combination of the deterministic path pruning followed by random short cut algorithm, as this in my experience performs better (in terms of how much it can optimize in a given time) then using just short cutting.

\vspace{0.5cm}

\textbf{Answer}:

We thank the reviewer for the suggestion of using Prune as a preliminary optimization step for each optimizer. Regarding to our algorithm, Prune has pros and cons: its removes waypoints i.e. optimization variables so the computation time reduces. However, less waypoints results in less possible actions to blend the path and bypass obstacles. In fact, we have noted that we often obtain shorter paths without the pruning stage.

In the article, we have added a brief comparison of two convergence graphs, with and without a preliminary pruning. This comparison just relates the gain in terms of computation time. We prefer not extend this part, because the main idea of the paper is not to discuss on the relevance of the Prune use.

\noindent
\hrulefill\\

@@

\subsection{Comment 1}

1) Notation and clarity of the presentation:

When introducing the Jacobian of f, at no point has f been introduced as the constraint function. I think in general the problem should be introduced as an optimization problem, what is the objective, what are the constraints, what simplifications will be made.

\vspace{0.5cm}

\textbf{Answer}:

We thank the reviewer for the remark and have removed the unreferenced objects.
We have improved the introduction of the problem, noting that the QP elements will be defined in the different parts of section 3. However, we prefer not give these definitions separately in a few rigorous subparts, as often encountered in the literature. We rather explain our motivations to insert constraints while encountering collisions, what type of constraint and how it allows to avoid the collision. Same argument is involved for the convergence analysis part.

\noindent
\hrulefill\\

\subsection{Comment 2}

@@

\noindent
\hrulefill\\

\subsection{Comment 3}

I wonder if the discussion concerning the configuration space, which is well done by the way, is of importance here, it is a perquisite in the robotics community.

\vspace{0.5cm}

\textbf{Answer}:

We want to highlight the fact that we optimize paths on the robot 
configuration space in a proper mathematical way, specially regarding to the $SO(3)$ rotations. Thus we prefer to briefly define notations and operators.

\noindent
\hrulefill\\

\subsection{Comment 4}

@@

\noindent
\hrulefill\\

\subsection{Comment 5}

The kernel discussion, and velocity discussion are a bit breve and unclear for the reader.

\vspace{0.5cm}

\textbf{Answer}:

The authors agree with the reviewer that this part should be modified as it is unclear. We add the Figure 5 to help understanding the interest of the convergence analysis of the 3.6 section. This latter section has been rewritten to clarify the link between the contact-point velocity and the constraint redundancy. Properties highlight the result of the analysis, that under some assumptions the additional loop in the global algorithm converges.

\noindent
\hrulefill\\

\subsection{Comment 6}

@@

\vspace{0.5cm}

\textbf{Answer}:

The unfair comparison, also raised by the reviewer 1, has been improved: we allocate the Gradient-Based duration as the computation times for the random optimizers. Thus we avoid arbitrary termination condition.

The drawback of this method is that we ignore whether the convergence rate of our method is in the same order of magnitude than RS and PRS. Thus, as suggested, we have represented the convergence curves for some benchmarks. Averages curves for RS and PRS, rather than just one try as in the trajectories Figures, are provided.

\noindent
\hrulefill\\

\subsection{Comment 7}

@@

Otherwise it would be interesting to see the alpha parameter being discussed at that point in the paper (with experimental results to back up the discussion).

\vspace{0.5cm}

\textbf{Answer}:

As suggested, we have added a section in the results parts gathering convergence graphs for different values of $\alpha_{init}$.
